Is Crime Really On A Rise In Toronto? An Analysis of The Past And Current Crime Rates of Toronto

### 2024-01-19 outputs/paper/paper.qmd
updated paper

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

average_crime_rates_per_year <- read_csv("outputs/data/average_crime_rates_data.csv")

@@

# Reading the data
percentage_change_data <- read_csv("outputs/data/percentage_change_data.csv")

@@

# Reading the data
final_percentage_change_table <- read.csv("outputs/data/percentage_change_table_2014_2023.csv")
```

@@

percentage_change_table <- read.csv("outputs/data/percentage_change_table_2022_2023.csv")
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

@@

@@

average_crime_rates_per_year <- read_csv(here::here("outputs/data/average_crime_rates_data.csv"))

@@

# Reading the data
percentage_change_data <- read_csv(here::here("outputs/data/percentage_change_data.csv"))

@@

# Reading the data
final_percentage_change_table <- read.csv(here::here("outputs/data/percentage_change_table_2014_2023.csv"))
```

@@

percentage_change_table <- read.csv(here::here("outputs/data/percentage_change_table_2022_2023.csv"))
```

@@

@@
